Redundant calibration as a complex optimization problem

### 2017-01-11 paper.tex
started working on section 5 again

\section{Results}
\label{sec:results}
In this section we compare the computational complexity of two newly proposed speedup algorithms for redundant calibration, namely the ADI \citep{Marthi2014} and PCG \citep{Liu2010} methods. We restrict ourselves to comparing the most 
expensive operation of the two methods namely, computing the inverse of the Hessian $\bH$ (or modified Hessian $\bmH$ in the case of LM). It becomes trivial to rate these two 
algorithms relative to each other once the computational complexity of the inverse operation is known. The simulations we performed to compare these two 
methods are summarized in Section~\ref{sec:simulations}.

@@

As we mention in Section~\ref{sec:results}, inspecting Fig.~\ref{fig:hessian} (also see Eq.~\eqref{eq:red_H}) reveals that in the case of redundant calibration the Hessian's diagonal entries are more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$.
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

@@

\section{Skymodel-based Calibration}
\label{sec:sbc}
\textsc{StEFCal} is an alternating direction implicit method, in which the measurement equation, Eq.~\eqref{eq:vis_definition}, is linearized by assuming that the gains are known, but
that their conjugates are unknown \citep{Mitchell:MWA-cal,Salvini2014}. Under this assumption, the conjugates of the gains can be obtained trivially. Once the conjugates of the gains have been computed, the gains can be solved for. One can then alternate between computing the gains and their conjugates until convergence
is reached. By correctly exploiting the symmetry inherent in the calibration problem this alternating approach can be replaced by a single iterative new parameter estimation step. \cite{Salvini2014} also show that
the convergence of the algorithm can be improved if for every even iteration the basic new parameter estimation step is modified as follows: the current gain estimate is replaced by the average of the current gain estimate and the gain estimate of the previous odd iteration.
\textsc{StEFCal} lowers the computational complexity of normal skymodel-based calibration from $\mathbb{O}(N^3)$ to $\mathbb{O}(N^2)$.

>>>>

\section{Results}
\label{sec:results}
In the previous section we discussed the complex GN and LM algorithms and how they relate to redundant calibration. If we inspect Eq.~\eqref{eq:GN_update} and 
Eq.~\eqref{eq:GN_update} we see that the most expensive operation used by the GN and LM algorithms is the inversion of the Hessian $\bH$. The most logical 
way of speeding up the algorithm is to investigate whether we can do this inversion in some efficient way.

Two recent algorithms have been proposed that are able to invert $\bH$ in an efficient manner, namely the ADI \citep{Marthi2014} and PCG \citep{Liu2010} methods. 
We restrict ourselves to comparing the most 
expensive operation of the two methods namely, computing the inverse of the Hessian $\bH$ (or modified Hessian $\bmH$ in the case of LM). It becomes trivial to rate these two 
algorithms relative to each other once the computational complexity of the inverse operation is known. The simulations we performed to compare these two 
methods are summarized in Section~\ref{sec:simulations}.

@@

\subsubsection{Skymodel-based Calibration}
\label{sec:sbc}
\textsc{StEFCal} is an alternating direction implicit method, in which the measurement equation, Eq.~\eqref{eq:vis_definition}, is linearized by assuming that the gains are known, but
that their conjugates are unknown \citep{Mitchell:MWA-cal,Salvini2014}. Under this assumption, the conjugates of the gains can be obtained trivially. Once the conjugates of the gains have been computed, the gains can be solved for. One can then alternate between computing the gains and their conjugates until convergence
is reached. By correctly exploiting the symmetry inherent in the calibration problem this alternating approach can be replaced by a single iterative new parameter estimation step. \cite{Salvini2014} also show that
the convergence of the algorithm can be improved if for every even iteration the basic new parameter estimation step is modified as follows: the current gain estimate is replaced by the average of the current gain estimate and the gain estimate of the previous odd iteration.
\textsc{StEFCal} lowers the computational complexity of normal skymodel-based calibration from $\mathbb{O}(N^3)$ to $\mathbb{O}(N^2)$.

\subsubsection{Redundant Calibration}
As we mention in Section~\ref{sec:results}, inspecting Fig.~\ref{fig:hessian} (also see Eq.~\eqref{eq:red_H}) reveals that in the case of redundant calibration the Hessian's diagonal entries are more significant than its off-diagonal entries.
If we substitute $\bJ^H\bJ$ with $\widetilde{\bH}$ (by its diagonal approximation) and replace $\breve{\br}$ with $\breve{\bd} - \breve{\bv}$ in Eq.~\eqref{eq:GN_update} we obtain
\begin{equation}
\label{eq:appr_GN}
 \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H(\breve{\bd}-\breve{\bv})
\end{equation}
Utilizing the second identity in Eq.~\eqref{eq:identities} allows us to simplify Eq.~\eqref{eq:appr_GN} to
\begin{equation}
  \Delta \breve{\bz} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}-\breve{\bz}.
\end{equation}
It now trivially follows that
\begin{equation}
 \breve{\bz}_{k+1} \approx \widetilde{\bH}^{-1}\bJ^H\breve{\bd}.
\end{equation}
We obtain a similar result if we repeat the above procedure, only in this case we use Eq.~\eqref{eq:LM_update} instead,
namely
\begin{align}
\breve{\bz}_{k+1} &\approx \frac{1}{1+\lambda}\widetilde{\bH}^{-1}\bJ^H\breve{\bd} + \frac{\lambda}{1+\lambda} \breve{\bz}_k,\label{eq:lambda}\\
 &= \alpha \widetilde{\bH}^{-1}\bJ^H\breve{\bd} + (1-\alpha)\breve{\bz}_k, \label{eq:alpha}  
\end{align}
where $\alpha = \frac{1}{1+\lambda}$. Moreover, $\lambda = \frac{1-\alpha}{\alpha}$.
The analytic expression of $\bJ^H\breve{\bd}$ will be very similar to the analytic 
expression of $\bJ^H\breve{\br}$, the only difference being that in Eq.~\eqref{eq:ab} the letter $r$ would be replaced by a $d$. If we substitute the analytic expression
of $\bJ^H\breve{\bd}$ and $\widetilde{\bH}^{-1}$ (which is easily computed as the matrix is a diagonal matrix) into Eq.~\eqref{eq:alpha} we obtain the following two update rules:
\begin{equation}
\label{eq:g_update}
g_{i}^{k+1} = \alpha \frac{\sum_{j\neq i} g_j^k \widetilde{y}_{ij}^{~\!\!k} d_{ij}}{\sum_{j\neq i} |g_j^k|^2|y_{\zeta_{ij}}^k|^2} + (1-\alpha) g_i^k, 
\end{equation}
and
\begin{equation}
\label{eq:y_update}
y_{i}^{k+1} = \alpha \frac{\sum_{pq \in \mathcal{PQ}_i} \conj{g}_p^k g_q^k d_{pq}}{\sum_{pq \in \mathcal{PQ}_i}|g_p^k|^2|g_q^k|^2} + (1-\alpha) y_i^k. 
\end{equation}
The computational complexity of inverting $\widetilde{\bH}$ is $\mathbb{O}(P)$.

@@
